To Be Decided

### 2024-08-21 main.tex
Inserção das imagens reconstruídas do primeiro estudo de caso dos experimentos sobre o indicador de forma

			\subsubsection{Single scatter}\label{sec:results:shape:star}

@@

                The following algorithms and their configurations were considered for this study:
                \begin{itemize}
                    \item Linear Sampling Method (LSM):
                    \begin{itemize}
                        \item Threshold: 0.7;
                        \item Regularization Method: Conjugate Gradient with 300 iterations.
                    \end{itemize}
                    \item Orthogonality Sampling Method (OSM):
                    \begin{itemize}
                        \item Threshold: 0.35;
                    \end{itemize}
                    \item Born Iterative Method (BIM):
                    \begin{itemize}
                        \item Regularization Method: Conjugate Gradient with 300 iterations.
                        \item Stopping Criterion: 30 iterations.
                    \end{itemize}
                    \item Contrast Source Inversion (CSI):
                    \begin{itemize}
                        \item Stopping Criterion: 300 iterations.
                    \end{itemize}
                    \item Subspace Optimization Method (SOM):
                    \begin{itemize}
                        \item Stopping Criterion: 30 iterations.
                        \item Eigenvalue Cutoff Index: 5.
                    \end{itemize}
                \end{itemize}

>>>>

			\subsubsection{Single scatterer}\label{sec:results:shape:star}

@@

                For this experiment, the following algorithms were considered: LSM, OSM, BIM, CSI, and SOM. Their parameters were chosen after empirical tests that aimed to achieve their best performance. The configurations for each algorithm are as follows:
                \begin{itemize}
                    \item Linear Sampling Method (LSM):
                    \begin{itemize}
                        \item Threshold: 0.7;
                        \item Regularization Method: Conjugate Gradient with 300 iterations.
                    \end{itemize}
                    \item Orthogonality Sampling Method (OSM):
                    \begin{itemize}
                        \item Threshold: 0.35;
                    \end{itemize}
                    \item Born Iterative Method (BIM):
                    \begin{itemize}
                        \item Regularization Method: Conjugate Gradient with 300 iterations.
                        \item Stopping Criterion: 30 iterations.
                    \end{itemize}
                    \item Contrast Source Inversion (CSI):
                    \begin{itemize}
                        \item Stopping Criterion: 300 iterations.
                    \end{itemize}
                    \item Subspace Optimization Method (SOM):
                    \begin{itemize}
                        \item Stopping Criterion: 30 iterations.
                        \item Eigenvalue Cutoff Index: 5.
                    \end{itemize}
                \end{itemize}

                The images reconstructed by each algorithm are shown in Fig. \ref{fig:shape:single:recons}.

                \begin{figure*}
                    \subfigure[Ground-Truth]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/0}}
                    \subfigure[LSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/1}}
                    \subfigure[OSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/2}} \\
                    \subfigure[BIM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/3}}
                    \subfigure[CSI]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/4}}
                    \subfigure[SOM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/5}}
                    \caption{Shape recovering study, single scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:shape:single:recons}
                \end{figure*}
